PANCHANGE_data_preprocessing

### 2020-08-12 PANCHANGE_data_preprocessing2020-07-15.Rmd
changed mhd object name

# glad mhd

```{r glad mhd cols}
glad.mhd.raw <- readRDS(file = paste0(data.raw_path,"/glad/mhd_glad.rds"))
dim(glad.mhd.raw)
colnames(glad.mhd.raw)
```

```{r glad mhd cleaning}
glad.mhd.raw.id <- glad.mhd.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID),
         startDate.prepandemic = startDate) %>% # Rename startDate
  select(
    Sample, # Sample
    ID, # ID
    starts_with("mhd.")
  ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

# Inspect dimensions
dim(glad.mhd.raw.id)
# Inspect colnames
colnames(glad.mhd.raw.id)
#Differences
dim(glad.mhd.raw)[1]-dim(glad.mhd.raw.id)[1]
```

@@

```{r glad mhd depressive_disorders}
glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    depressive_disorders_numeric =
      case_when(
        (mhd.depression_numeric == "0" &
        (mhd.pregnancy_depression_numeric == "0" | is.na(mhd.pregnancy_depression_numeric)) & 
        (mhd.premenstrual_dysphoric_disorder_pmdd_numeric == "0" | is.na(mhd.premenstrual_dysphoric_disorder_pmdd_numeric))) ~ 0,
        mhd.depression_numeric == "1" ~ 1,
        mhd.pregnancy_depression_numeric == "1" ~ 1,
        mhd.premenstrual_dysphoric_disorder_pmdd_numeric == "1" ~ 1))

glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    depressive_disorders =
      recode_factor(depressive_disorders_numeric,
                    "0" = "No depressive disorder",
                    "1" = "Depressive disorder",
                    missing = NA_character_
                    )
  )

glad.mhd.raw.id %>%
  freq(depressive_disorders,
       cumul = F)
```

```{r Check depressive_disorders}
glad.mhd.raw.id %>%
  select(
    depressive_disorders,
    depressive_disorders_numeric,
    mhd.depression_numeric,
    mhd.pregnancy_depression_numeric,
    mhd.premenstrual_dysphoric_disorder_pmdd_numeric,
    mhd.depression,
    mhd.pregnancy_depression,
    mhd.premenstrual_dysphoric_disorder_pmdd
  )
```

Anxiety disorders group
```{r glad mhd anxiety_disorders}
glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    anxiety_disorders_numeric =
      case_when(
        mhd.anxiety_nerves_or_generalised_anxiety_disorder_numeric == "1" ~ 1,
        mhd.social_anxiety_or_social_phobia_numeric == "1" ~ 1,
        mhd.specific_phobia_e.g._phobia_of_flying_numeric == "1" ~ 1,
        mhd.agoraphobia_numeric == "1" ~ 1,
        mhd.panic_disorder_numeric == "1" ~ 1,
        mhd.panic_attacks_numeric == "1" ~ 1,
        (mhd.anxiety_nerves_or_generalised_anxiety_disorder_numeric == "0" &
        mhd.social_anxiety_or_social_phobia_numeric == "0" &
        mhd.specific_phobia_e.g._phobia_of_flying_numeric == "0" &
        mhd.agoraphobia_numeric == "0" &
        mhd.panic_disorder_numeric == "0" &
        mhd.panic_attacks_numeric == "0") ~ 0
      )
  )

glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    anxiety_disorders =
      recode_factor(anxiety_disorders_numeric,
                    "0" = "No anxiety disorder",
                    "1" = "Anxiety disorder",
                    missing = NA_character_
                    )
  )

glad.mhd.raw.id %>%
  freq(anxiety_disorders,
       cumul = F)
```

```{r Check anxiety_disorders}
glad.mhd.raw.id %>%
  select(
    anxiety_disorders,
    anxiety_disorders_numeric,
    mhd.anxiety_nerves_or_generalised_anxiety_disorder_numeric,
    mhd.social_anxiety_or_social_phobia_numeric,
    mhd.specific_phobia_e.g._phobia_of_flying_numeric,
    mhd.agoraphobia_numeric,
    mhd.panic_disorder_numeric,
    mhd.panic_attacks_numeric,
    mhd.anxiety_nerves_or_generalised_anxiety_disorder,
    mhd.social_anxiety_or_social_phobia,
    mhd.specific_phobia_e.g._phobia_of_flying,
    mhd.agoraphobia,
    mhd.panic_disorder,
    mhd.panic_attacks
  )
```

Agoraphonia and panic disorder group
```{r glad mhd agoraphobia_panic_disorder}
glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    agoraphobia_panic_disorder_numeric =
      case_when(
        mhd.agoraphobia_numeric == "1" ~ 1,
        mhd.panic_disorder_numeric == "1" ~ 1,
        mhd.panic_attacks_numeric == "1" ~ 1,
        (mhd.agoraphobia_numeric == "0" &
        mhd.panic_disorder_numeric == "0" &
        mhd.panic_attacks_numeric == "0") ~ 0
      )
  )

glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    agoraphobia_panic_disorder =
      recode_factor(agoraphobia_panic_disorder_numeric,
                    "0" = "No agoraphobia/panic disorder",
                    "1" = "Agoraphobia/panic disorder",
                    missing = NA_character_
                    )
  )

glad.mhd.raw.id %>%
  freq(agoraphobia_panic_disorder)
```

```{r Check agoraphobia_panic_disorder}
glad.mhd.raw.id %>%
  select(
    agoraphobia_panic_disorder,
    agoraphobia_panic_disorder_numeric,
    mhd.agoraphobia_numeric,
    mhd.panic_disorder_numeric,
    mhd.panic_attacks_numeric,
    mhd.agoraphobia,
    mhd.panic_disorder,
    mhd.panic_attacks
  )
```

Depression and anxiety comorbidity
```{r glad mhd depression_anxiety}
glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    depression_and_anxiety_numeric =
      case_when(
        depressive_disorders_numeric == 0 &
          anxiety_disorders_numeric == 0 ~ 0,
        depressive_disorders_numeric == 1 &
          anxiety_disorders_numeric == 1 ~ 1,
        depressive_disorders_numeric == 1 &
          anxiety_disorders_numeric == 0 ~ 2,
        depressive_disorders_numeric == 0 &
          anxiety_disorders_numeric == 1 ~ 3
      )
  )

glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    depression_and_anxiety =
      recode_factor(depression_and_anxiety_numeric,
                    "0" = "No depressive or anxiety disorder",
                    "1" = "Depressive and anxiety disorder",
                    "2" = "Only depressive disorder",
                    "2" = "Only anxiety disorder",
                    missing = NA_character_
                    )
  )

glad.mhd.raw.id %>%
  freq(depression_and_anxiety,
       cumul = F)
```

Eating disorders group
```{r glad mhd eating_disorders}
glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    eating_disorders_numeric =
      case_when(
        mhd.anorexia_nervosa_numeric == "1" ~ 1,
        mhd.atypical_anorexia_nervosa_numeric == "1" ~ 1,
        mhd.bulimia_nervosa_numeric == "1" ~ 1,
        mhd.psychological_overeating_or_bingeeating_numeric == "1" ~ 1,
        (mhd.anorexia_nervosa_numeric == "0" &
        mhd.atypical_anorexia_nervosa_numeric == "0" &
        mhd.bulimia_nervosa_numeric == "0" &
        mhd.psychological_overeating_or_bingeeating_numeric == "0") ~ 0
      )
  )

glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    eating_disorders =
      recode_factor(eating_disorders_numeric,
                    "0" = "No eating disorder",
                    "1" = "Eating disorder",
                    missing = NA_character_
                    )
  )

glad.mhd.raw.id %>%
  freq(eating_disorders,
       cumul = F)
```

Eating disorders with binge eating vs eating disorders without
Caveat: Anorexia nervosa can have binge eating as well. Therefore, this would need an additional variable from the ED100K
```{r glad mhd restricting_vs_binge_eating_eating_disorders}
glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    restricting_vs_binge_eating_eating_disorders_numeric =
      case_when(
                mhd.anorexia_nervosa_numeric == "1" ~ 1,
        mhd.atypical_anorexia_nervosa_numeric == "1" ~ 1,
        mhd.bulimia_nervosa_numeric == "1" ~ 2,
        mhd.psychological_overeating_or_bingeeating_numeric == "1" ~ 2,
        (mhd.anorexia_nervosa_numeric == "0" &
        mhd.atypical_anorexia_nervosa_numeric == "0" &
        mhd.bulimia_nervosa_numeric == "0" &
        mhd.psychological_overeating_or_bingeeating_numeric == "0") ~ 0
      )
  )

glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    restricting_vs_binge_eating_eating_disorders =
      recode_factor(restricting_vs_binge_eating_eating_disorders_numeric,
                    "0" = "No eating disorder",
                    "1" = "Anorexia nervosa",
                    "2" = "Eating disorder with binge eating",
                    missing = NA_character_
                    )
  )

glad.mhd.raw.id %>%
  freq(restricting_vs_binge_eating_eating_disorders,
       cumul = F)
```

```{r Check eating_disorders}
glad.mhd.raw.id %>%
  select(
    eating_disorders,
    eating_disorders_numeric,
    restricting_vs_binge_eating_eating_disorders,
    restricting_vs_binge_eating_eating_disorders_numeric,
    mhd.anorexia_nervosa_numeric,
    mhd.atypical_anorexia_nervosa_numeric,
    mhd.bulimia_nervosa_numeric,
    mhd.psychological_overeating_or_bingeeating_numeric,
    mhd.anorexia_nervosa,
    mhd.atypical_anorexia_nervosa,
    mhd.bulimia_nervosa,
    mhd.psychological_overeating_or_bingeeating
  )
```

Obsessive compulsive disorders
```{r glad mhd obsessive_compulsive_disorders}
glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    obsessive_compulsive_disorders_numeric =
      case_when(
        mhd.obsessivecompulsive_disorder_ocd_numeric == "1" ~ 1,
        mhd.obsessive_compulsive_related_disorders_numeric == "1" ~ 1,
        mhd.body_dysmorphic_disorder_bdd_numeric == "1" ~ 1,
        (mhd.obsessivecompulsive_disorder_ocd_numeric == "0" &
        mhd.obsessive_compulsive_related_disorders_numeric == "0" &
        mhd.body_dysmorphic_disorder_bdd_numeric == "0") ~ 0
      )
  )

glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    obsessive_compulsive_disorders =
      recode_factor(obsessive_compulsive_disorders_numeric,
                    "0" = "No obsessivecompulsive disorder",
                    "1" = "Obsessive compulsive disorder",
                    missing = NA_character_
                    )
  )

glad.mhd.raw.id %>%
  freq(obsessive_compulsive_disorders)
```

```{r Check obsessive_compulsive_disorders}
glad.mhd.raw.id %>%
  select(
    obsessive_compulsive_disorders,
    obsessive_compulsive_disorders_numeric,
    mhd.obsessivecompulsive_disorder_ocd,
    mhd.obsessivecompulsive_disorder_ocd_numeric,
    mhd.obsessive_compulsive_related_disorders,
    mhd.obsessive_compulsive_related_disorders_numeric
  )
```

Psychotic disorders group
[63] "mhd.schizophrenia_numeric"                                 
[64] "mhd.schizoaffective_disorder_numeric"                      
[65] "mhd.type_psychosis_psychotic_illness_numeric" 
```{r glad mhd psychotic_disorders}
glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    psychotic_disorders_numeric =
      case_when(
        mhd.schizophrenia_numeric == "1" ~ 1,
        mhd.schizoaffective_disorder_numeric == "1" ~ 1,
        mhd.type_psychosis_psychotic_illness_numeric == "1" ~ 1,
        (mhd.schizophrenia_numeric == "0" &
        mhd.schizoaffective_disorder_numeric == "0" &
        mhd.type_psychosis_psychotic_illness_numeric == "0") ~ 0
      )
  )

glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    psychotic_disorders =
      recode_factor(psychotic_disorders_numeric,
                    "0" = "No psychotic disorder",
                    "1" = "Psychotic disorder",
                    missing = NA_character_
                    )
  )

glad.mhd.raw.id %>%
  freq(psychotic_disorders)
```

Overlap between self-report schizophrenia and bipolar disorder
+++CH: Check overlap between schizophrenia group and bipolar disorder
++KT: Only 63 with comorbid self-report bipolar disorder and schizophrenia. More likely to have shared symptoms, less likely to have confirmed diagnoses of both. Could be too severe to be in GLAD?
```{r glad mhd bipolar_and_schizophrenia_numeric}
glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    bipolar_and_schizophrenia_numeric =
      case_when(
        psychotic_disorders_numeric == 0 &
          mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 0 ~ 0,
                psychotic_disorders_numeric == 1 &
          mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 0 ~ 2,
        psychotic_disorders_numeric == 0 &
          mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 3,
                psychotic_disorders_numeric == 1 &
          mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 1
      )
  )

glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    bipolar_and_schizophrenia =
      recode_factor(bipolar_and_schizophrenia_numeric,
                    "0" = "No psychotic or bipolar disorder",
                    "1" = "Psychotic and bipolar disorder",
                    "2" = "Only psychotic disorder",
                    "3" = "Only bipolar disorder",
                    missing = NA_character_
                    )
  )

glad.mhd.raw.id %>%
  freq(bipolar_and_schizophrenia,
       cumul = F)
```

```{r Check psychotic_disorders}
glad.mhd.raw.id %>%
  select(
    psychotic_disorders,
    psychotic_disorders_numeric,
    bipolar_and_schizophrenia,
    bipolar_and_schizophrenia_numeric,
    mhd.schizophrenia_numeric,
    mhd.schizoaffective_disorder_numeric,
    mhd.mania_hypomania_bipolar_or_manicdepression,
    mhd.mania_hypomania_bipolar_or_manicdepression_numeric,
    mhd.type_psychosis_psychotic_illness_numeric,
    mhd.schizophrenia,
    mhd.schizoaffective_disorder,
    mhd.type_psychosis_psychotic_illness
  )
```

Personality disorder groups
++KT: For all cluster coding chunks - have added other clusters as == 0, so that they are not coerced into NAs. 
Cluster A
1. Paranoid                         28 ( 1.0%)
2. Schizoid                         15 ( 0.5%)
3. Schizotypal                      14 ( 0.5%)
```{r glad mhd personality_cluster_a}
glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    personality_cluster_a_numeric =
      case_when(
        mhd.personality_disorder_diagnosed_numeric == "1" ~ 1,
        mhd.personality_disorder_diagnosed_numeric == "2" ~ 1,
        mhd.personality_disorder_diagnosed_numeric == "3" ~ 1,
        mhd.personality_disorder_diagnosed_numeric == "4" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "5" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "6" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "7" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "8" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "9" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "10" ~ 0,
        mhd.personality_disorder_numeric == "0" ~ 0
      )
  )

>>>>

# mhd

## GLAD
```{r glad mhd cols}
if(GLAD == TRUE) {
glad.mhd.raw <- readRDS(file = paste0(data.raw_path,"/glad/mhd_glad.rds"))
dim(glad.mhd.raw)
colnames(glad.mhd.raw)
}
```

```{r glad mhd cleaning}
if(GLAD == TRUE) {
glad.mhd.raw.id <- glad.mhd.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID),
         startDate.prepandemic = startDate) %>% # Rename startDate
  select(
    Sample, # Sample
    ID, # ID
    starts_with("mhd.")
  ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

# Inspect dimensions
dim(glad.mhd.raw.id)
# Inspect colnames
colnames(glad.mhd.raw.id)
#Differences
dim(glad.mhd.raw)[1]-dim(glad.mhd.raw.id)[1]
}
```

@@

```{r glad mhd depressive_disorders}
mhd.raw.id <- mhd.raw.id %>%
  mutate(
    depressive_disorders_numeric =
      case_when(
        (mhd.depression_numeric == "0" &
        (mhd.pregnancy_depression_numeric == "0" | is.na(mhd.pregnancy_depression_numeric)) & 
        (mhd.premenstrual_dysphoric_disorder_pmdd_numeric == "0" | is.na(mhd.premenstrual_dysphoric_disorder_pmdd_numeric))) ~ 0,
        mhd.depression_numeric == "1" ~ 1,
        mhd.pregnancy_depression_numeric == "1" ~ 1,
        mhd.premenstrual_dysphoric_disorder_pmdd_numeric == "1" ~ 1))

mhd.raw.id <- mhd.raw.id %>%
  mutate(
    depressive_disorders =
      recode_factor(depressive_disorders_numeric,
                    "0" = "No depressive disorder",
                    "1" = "Depressive disorder",
                    missing = NA_character_
                    )
  )

mhd.raw.id %>%
  freq(depressive_disorders,
       cumul = F)
```

```{r Check depressive_disorders}
mhd.raw.id %>%
  select(
    depressive_disorders,
    depressive_disorders_numeric,
    mhd.depression_numeric,
    mhd.pregnancy_depression_numeric,
    mhd.premenstrual_dysphoric_disorder_pmdd_numeric,
    mhd.depression,
    mhd.pregnancy_depression,
    mhd.premenstrual_dysphoric_disorder_pmdd
  )
```

Anxiety disorders group
```{r glad mhd anxiety_disorders}
mhd.raw.id <- mhd.raw.id %>%
  mutate(
    anxiety_disorders_numeric =
      case_when(
        mhd.anxiety_nerves_or_generalised_anxiety_disorder_numeric == "1" ~ 1,
        mhd.social_anxiety_or_social_phobia_numeric == "1" ~ 1,
        mhd.specific_phobia_e.g._phobia_of_flying_numeric == "1" ~ 1,
        mhd.agoraphobia_numeric == "1" ~ 1,
        mhd.panic_disorder_numeric == "1" ~ 1,
        mhd.panic_attacks_numeric == "1" ~ 1,
        (mhd.anxiety_nerves_or_generalised_anxiety_disorder_numeric == "0" &
        mhd.social_anxiety_or_social_phobia_numeric == "0" &
        mhd.specific_phobia_e.g._phobia_of_flying_numeric == "0" &
        mhd.agoraphobia_numeric == "0" &
        mhd.panic_disorder_numeric == "0" &
        mhd.panic_attacks_numeric == "0") ~ 0
      )
  )

mhd.raw.id <- mhd.raw.id %>%
  mutate(
    anxiety_disorders =
      recode_factor(anxiety_disorders_numeric,
                    "0" = "No anxiety disorder",
                    "1" = "Anxiety disorder",
                    missing = NA_character_
                    )
  )

mhd.raw.id %>%
  freq(anxiety_disorders,
       cumul = F)
```

```{r Check anxiety_disorders}
mhd.raw.id %>%
  select(
    anxiety_disorders,
    anxiety_disorders_numeric,
    mhd.anxiety_nerves_or_generalised_anxiety_disorder_numeric,
    mhd.social_anxiety_or_social_phobia_numeric,
    mhd.specific_phobia_e.g._phobia_of_flying_numeric,
    mhd.agoraphobia_numeric,
    mhd.panic_disorder_numeric,
    mhd.panic_attacks_numeric,
    mhd.anxiety_nerves_or_generalised_anxiety_disorder,
    mhd.social_anxiety_or_social_phobia,
    mhd.specific_phobia_e.g._phobia_of_flying,
    mhd.agoraphobia,
    mhd.panic_disorder,
    mhd.panic_attacks
  )
```

Agoraphonia and panic disorder group
```{r glad mhd agoraphobia_panic_disorder}
mhd.raw.id <- mhd.raw.id %>%
  mutate(
    agoraphobia_panic_disorder_numeric =
      case_when(
        mhd.agoraphobia_numeric == "1" ~ 1,
        mhd.panic_disorder_numeric == "1" ~ 1,
        mhd.panic_attacks_numeric == "1" ~ 1,
        (mhd.agoraphobia_numeric == "0" &
        mhd.panic_disorder_numeric == "0" &
        mhd.panic_attacks_numeric == "0") ~ 0
      )
  )

mhd.raw.id <- mhd.raw.id %>%
  mutate(
    agoraphobia_panic_disorder =
      recode_factor(agoraphobia_panic_disorder_numeric,
                    "0" = "No agoraphobia/panic disorder",
                    "1" = "Agoraphobia/panic disorder",
                    missing = NA_character_
                    )
  )

mhd.raw.id %>%
  freq(agoraphobia_panic_disorder)
```

```{r Check agoraphobia_panic_disorder}
mhd.raw.id %>%
  select(
    agoraphobia_panic_disorder,
    agoraphobia_panic_disorder_numeric,
    mhd.agoraphobia_numeric,
    mhd.panic_disorder_numeric,
    mhd.panic_attacks_numeric,
    mhd.agoraphobia,
    mhd.panic_disorder,
    mhd.panic_attacks
  )
```

Depression and anxiety comorbidity
```{r glad mhd depression_anxiety}
mhd.raw.id <- mhd.raw.id %>%
  mutate(
    depression_and_anxiety_numeric =
      case_when(
        depressive_disorders_numeric == 0 &
          anxiety_disorders_numeric == 0 ~ 0,
        depressive_disorders_numeric == 1 &
          anxiety_disorders_numeric == 1 ~ 1,
        depressive_disorders_numeric == 1 &
          anxiety_disorders_numeric == 0 ~ 2,
        depressive_disorders_numeric == 0 &
          anxiety_disorders_numeric == 1 ~ 3
      )
  )

mhd.raw.id <- mhd.raw.id %>%
  mutate(
    depression_and_anxiety =
      recode_factor(depression_and_anxiety_numeric,
                    "0" = "No depressive or anxiety disorder",
                    "1" = "Depressive and anxiety disorder",
                    "2" = "Only depressive disorder",
                    "2" = "Only anxiety disorder",
                    missing = NA_character_
                    )
  )

mhd.raw.id %>%
  freq(depression_and_anxiety,
       cumul = F)
```

Eating disorders group
```{r glad mhd eating_disorders}
mhd.raw.id <- mhd.raw.id %>%
  mutate(
    eating_disorders_numeric =
      case_when(
        mhd.anorexia_nervosa_numeric == "1" ~ 1,
        mhd.atypical_anorexia_nervosa_numeric == "1" ~ 1,
        mhd.bulimia_nervosa_numeric == "1" ~ 1,
        mhd.psychological_overeating_or_bingeeating_numeric == "1" ~ 1,
        (mhd.anorexia_nervosa_numeric == "0" &
        mhd.atypical_anorexia_nervosa_numeric == "0" &
        mhd.bulimia_nervosa_numeric == "0" &
        mhd.psychological_overeating_or_bingeeating_numeric == "0") ~ 0
      )
  )

mhd.raw.id <- mhd.raw.id %>%
  mutate(
    eating_disorders =
      recode_factor(eating_disorders_numeric,
                    "0" = "No eating disorder",
                    "1" = "Eating disorder",
                    missing = NA_character_
                    )
  )

mhd.raw.id %>%
  freq(eating_disorders,
       cumul = F)
```

Eating disorders with binge eating vs eating disorders without
Caveat: Anorexia nervosa can have binge eating as well. Therefore, this would need an additional variable from the ED100K
```{r glad mhd restricting_vs_binge_eating_eating_disorders}
mhd.raw.id <- mhd.raw.id %>%
  mutate(
    restricting_vs_binge_eating_eating_disorders_numeric =
      case_when(
                mhd.anorexia_nervosa_numeric == "1" ~ 1,
        mhd.atypical_anorexia_nervosa_numeric == "1" ~ 1,
        mhd.bulimia_nervosa_numeric == "1" ~ 2,
        mhd.psychological_overeating_or_bingeeating_numeric == "1" ~ 2,
        (mhd.anorexia_nervosa_numeric == "0" &
        mhd.atypical_anorexia_nervosa_numeric == "0" &
        mhd.bulimia_nervosa_numeric == "0" &
        mhd.psychological_overeating_or_bingeeating_numeric == "0") ~ 0
      )
  )

mhd.raw.id <- mhd.raw.id %>%
  mutate(
    restricting_vs_binge_eating_eating_disorders =
      recode_factor(restricting_vs_binge_eating_eating_disorders_numeric,
                    "0" = "No eating disorder",
                    "1" = "Anorexia nervosa",
                    "2" = "Eating disorder with binge eating",
                    missing = NA_character_
                    )
  )

mhd.raw.id %>%
  freq(restricting_vs_binge_eating_eating_disorders,
       cumul = F)
```

```{r Check eating_disorders}
mhd.raw.id %>%
  select(
    eating_disorders,
    eating_disorders_numeric,
    restricting_vs_binge_eating_eating_disorders,
    restricting_vs_binge_eating_eating_disorders_numeric,
    mhd.anorexia_nervosa_numeric,
    mhd.atypical_anorexia_nervosa_numeric,
    mhd.bulimia_nervosa_numeric,
    mhd.psychological_overeating_or_bingeeating_numeric,
    mhd.anorexia_nervosa,
    mhd.atypical_anorexia_nervosa,
    mhd.bulimia_nervosa,
    mhd.psychological_overeating_or_bingeeating
  )
```

Obsessive compulsive disorders
```{r glad mhd obsessive_compulsive_disorders}
mhd.raw.id <- mhd.raw.id %>%
  mutate(
    obsessive_compulsive_disorders_numeric =
      case_when(
        mhd.obsessivecompulsive_disorder_ocd_numeric == "1" ~ 1,
        mhd.obsessive_compulsive_related_disorders_numeric == "1" ~ 1,
        mhd.body_dysmorphic_disorder_bdd_numeric == "1" ~ 1,
        (mhd.obsessivecompulsive_disorder_ocd_numeric == "0" &
        mhd.obsessive_compulsive_related_disorders_numeric == "0" &
        mhd.body_dysmorphic_disorder_bdd_numeric == "0") ~ 0
      )
  )

mhd.raw.id <- mhd.raw.id %>%
  mutate(
    obsessive_compulsive_disorders =
      recode_factor(obsessive_compulsive_disorders_numeric,
                    "0" = "No obsessivecompulsive disorder",
                    "1" = "Obsessive compulsive disorder",
                    missing = NA_character_
                    )
  )

mhd.raw.id %>%
  freq(obsessive_compulsive_disorders)
```

```{r Check obsessive_compulsive_disorders}
mhd.raw.id %>%
  select(
    obsessive_compulsive_disorders,
    obsessive_compulsive_disorders_numeric,
    mhd.obsessivecompulsive_disorder_ocd,
    mhd.obsessivecompulsive_disorder_ocd_numeric,
    mhd.obsessive_compulsive_related_disorders,
    mhd.obsessive_compulsive_related_disorders_numeric
  )
```

Psychotic disorders group
[63] "mhd.schizophrenia_numeric"                                 
[64] "mhd.schizoaffective_disorder_numeric"                      
[65] "mhd.type_psychosis_psychotic_illness_numeric" 
```{r glad mhd psychotic_disorders}
mhd.raw.id <- mhd.raw.id %>%
  mutate(
    psychotic_disorders_numeric =
      case_when(
        mhd.schizophrenia_numeric == "1" ~ 1,
        mhd.schizoaffective_disorder_numeric == "1" ~ 1,
        mhd.type_psychosis_psychotic_illness_numeric == "1" ~ 1,
        (mhd.schizophrenia_numeric == "0" &
        mhd.schizoaffective_disorder_numeric == "0" &
        mhd.type_psychosis_psychotic_illness_numeric == "0") ~ 0
      )
  )

mhd.raw.id <- mhd.raw.id %>%
  mutate(
    psychotic_disorders =
      recode_factor(psychotic_disorders_numeric,
                    "0" = "No psychotic disorder",
                    "1" = "Psychotic disorder",
                    missing = NA_character_
                    )
  )

mhd.raw.id %>%
  freq(psychotic_disorders)
```

Overlap between self-report schizophrenia and bipolar disorder
+++CH: Check overlap between schizophrenia group and bipolar disorder
++KT: Only 63 with comorbid self-report bipolar disorder and schizophrenia. More likely to have shared symptoms, less likely to have confirmed diagnoses of both. Could be too severe to be in GLAD?
```{r glad mhd bipolar_and_schizophrenia_numeric}
mhd.raw.id <- mhd.raw.id %>%
  mutate(
    bipolar_and_schizophrenia_numeric =
      case_when(
        psychotic_disorders_numeric == 0 &
          mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 0 ~ 0,
                psychotic_disorders_numeric == 1 &
          mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 0 ~ 2,
        psychotic_disorders_numeric == 0 &
          mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 3,
                psychotic_disorders_numeric == 1 &
          mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 1
      )
  )

mhd.raw.id <- mhd.raw.id %>%
  mutate(
    bipolar_and_schizophrenia =
      recode_factor(bipolar_and_schizophrenia_numeric,
                    "0" = "No psychotic or bipolar disorder",
                    "1" = "Psychotic and bipolar disorder",
                    "2" = "Only psychotic disorder",
                    "3" = "Only bipolar disorder",
                    missing = NA_character_
                    )
  )

mhd.raw.id %>%
  freq(bipolar_and_schizophrenia,
       cumul = F)
```

```{r Check psychotic_disorders}
mhd.raw.id %>%
  select(
    psychotic_disorders,
    psychotic_disorders_numeric,
    bipolar_and_schizophrenia,
    bipolar_and_schizophrenia_numeric,
    mhd.schizophrenia_numeric,
    mhd.schizoaffective_disorder_numeric,
    mhd.mania_hypomania_bipolar_or_manicdepression,
    mhd.mania_hypomania_bipolar_or_manicdepression_numeric,
    mhd.type_psychosis_psychotic_illness_numeric,
    mhd.schizophrenia,
    mhd.schizoaffective_disorder,
    mhd.type_psychosis_psychotic_illness
  )
```

Personality disorder groups
++KT: For all cluster coding chunks - have added other clusters as == 0, so that they are not coerced into NAs. 
Cluster A
1. Paranoid                         28 ( 1.0%)
2. Schizoid                         15 ( 0.5%)
3. Schizotypal                      14 ( 0.5%)
```{r glad mhd personality_cluster_a}
mhd.raw.id <- mhd.raw.id %>%
  mutate(
    personality_cluster_a_numeric =
      case_when(
        mhd.personality_disorder_diagnosed_numeric == "1" ~ 1,
        mhd.personality_disorder_diagnosed_numeric == "2" ~ 1,
        mhd.personality_disorder_diagnosed_numeric == "3" ~ 1,
        mhd.personality_disorder_diagnosed_numeric == "4" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "5" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "6" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "7" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "8" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "9" ~ 0,
        mhd.personality_disorder_diagnosed_numeric == "10" ~ 0,
        mhd.personality_disorder_numeric == "0" ~ 0
      )
  )

mhd.raw.id <- mhd.raw.id %>%
  mutate(
    personality_cluster_a =
      recode_factor(personality_cluster_a_numeric,
                    "0" = "No personality disorder cluster A",
                    "1" = "Personality disorder cluster A",
                    missing = NA_character_
                    )
  )

mhd.raw.id %>%
  freq(personality_cluster_a,
       cumul = F)
```
